\printbibliography

\chapter{Protocols - Cloning}
\section{BioBrick cloning}
\section{Mobius assembly}
\section{Loop assembly}
\section{Gibson cloning}
\section{Golden Gate cloning}


\chapter{Protocols - Transformation}
\section{Cyanobacteria}
\subsection{Indirect Methods}
\subsection{Direct Methods}
\section{Higher Plants}
\subsection{Indirect Methods}
\subsection{Direct Methods}
\section{Algae}
\subsection{Indirect Methods}
\subsection{Direct Methods}


\chapter{Protocols - Others}
\section{Media}
\subsection{BG11 and agar type A} 
\subsubsection{BG11 protocol}
Source: \href{https://www.protocols.io/view/bg11-medium-working-group-wilde-wj5fcq6}{https://www.protocols.io/view/bg11-medium-working-group-wilde-wj5fcq6}
\paragraph{NOTE}: Some of the chemicals used in the preparation of BG11 are carcinogenic. Use the appropriate safety gear. When aliquoting and sterile filtering the trace metal solution, do this in a fume hood with extra ventilation. There should be a BG11 waste container for any waste that is generated during the process - do not throw away things in the sink or any other waste system!
\subsubsection{Materials}
\paragraph{100x BG11:}
\begin{itemize}
    \item NaNO3
    \item MgSO4 x 7 H2O
    \item CaCl2 x 2 H2O
    \item Citric acid 
    \item Na2EDTA pH 8, 0.5 M
\end{itemize}

\paragraph{Trace metal mix:}
\begin{itemize}
    \item H3BO3
    \item MnCl2 x 2 H2O
    \item ZnSO4 x 2 H2O
    \item Na2MoO4 x 2 H2O
    \item CuSO4 x 5 H2O
    \item Co(NO3)2 x 6 H2O
\end{itemize}

\paragraph{1x BG11:}
\begin{itemize}
    \item TES buffer pH 8 (2M)
    \item K2HPO4 x 3H2O, 30 mg/mL 
    \item Na2CO3, 20 mg/mL 
\end{itemize}

\paragraph{Other:}
\begin{itemize}
    \item ddH2O 
    \item 9 x 100 mL flasks with screw-on lids (if aliquoting 1X BG11, 19 flasks are needed)
    \item Pipette tips
    \item 10 x 50 mL Falcon tubes
    \item 1 x 15 mL Falcon tube
    \item Plastic pasteur pipettes
    \item pH probe
    \item Scale
\end{itemize}

\subsubsection{Method}
\paragraph{100X BG11:}
\begin{enumerate}
    \item In a 500 mL flask, directly measure the following chemicals
\begin{enumerate}
    \item 74.79 g 	NaNO3
    \item 3.75 g 		MgSO4 x 7 H2O
    \item 1.8 g 		CaCl2 x 2 H2O
    \item 0.3 g 		Citric acid
\end{enumerate}
\item Add 0.28 mL Na2EDTA pH 8, 0.5 M to the 500 mL flask. 
\item Add ddH2O to a volume of 500 mL
\item Aliquot the mixture into 5 x 100 mL flasks.
\item Autoclave the aliquots 
\item Store the aliquots at 4°C(fridge)
\end{enumerate}

\paragraph{Trace metal mix:}
\begin{enumerate}
    \item In a 500 mL flask, directly measure the following chemicals
    \begin{enumerate}
        \item 1.43 g 		H3BO3
        \item 900 mg	MnCl2 x 4 H2O
        \item 110 mg 	ZnSO4 x 7 H2O
        \item 195 mg 	Na2MoO4 x 2 H2O
        \item 39.5 mg 	CuSO4 x 5 H2O
        \item 24.7 mg 	Co(NO3)2 x 6 H2O
\end{enumerate}
\item Add some ddH2O to the flask to dissolve the salts, then add ddH2O to a total volume of 500 mL 
\item Sterile filter the solution into 50 mL Falcon tubes. Each tube should contain 50 mL of the solution. 
\item Store the trace metal mix at 4°C. 
\end{enumerate}

\paragraph{1X BG11:}
\begin{enumerate}
    \item In a 1 L flask, add 500 mL ddH2O
    \item In the 1 L flask, add the following:
    \begin{enumerate}
        \item 10 mL 		100x BG-11 				
        \item 1 mL 		K2HPO4 x 3H2O (30 mg/mL) 		
        \item 1 mL 		Na2CO3 (20 mg/mL) 			
        \item 1 mL 		Trace metal solution 			
        \item 10 mL 		HEPES buffer pH 8 (2M) 	
\end{enumerate}
\item Adjust pH with NaOH to pH 8 
\item Add ddH2O to a final volume of 1 L
\item Aliquot to 10 x 100 mL 
\item Autoclave
\item Store in room temperature 
\end{enumerate}

\textbf{Before using 1X BG11}: Add 1mL 6 mg/mL citric acid to 100 mL 1 X BG11 

\pagebreak

\subsection{BG11 Agar Type A} 
\subsubsection{Materials}
\begin{itemize}
    \item 1 x BG11 
    \item Pipette tips
    \item Fe-ammonium citrate, concentration 6 mg/mL
    \item Agar type A powder
    \item Sterile plates 
    \item Flask
\end{itemize}

\textbf{NOTE}: Work under flame

\subsubsection{Method}
\begin{enumerate}
    \item Measure 3 g agar type A in a flask, add 250 mL, 1 x BG11, 50 µL 6 mg/mL Fe-ammonium citrate. 
    \item Autoclave the jar at 121°C. If needed, reheat the mixture to melt it after autoclaving, the solution has to be fully melted.  
    \item Use 50 mL falcon tubes to measure the volume needed for the plates, 30 mL. 
    \begin{enumerate}
        \item If antibiotics are needed, add them after the media has cooled enough to hold in your hand.
    \end{enumerate}
\item Pour the media to plates while it is still warm and in liquid form, put on the lid and wait until the media solidifies. 
\item Seal the plates with micropore tape.
\end{enumerate}
